The watershed transform in ITK - discussion and new developments

### 2006-05-23 article/Article.tex
Added label
darcs-hash:20060523062722-fafb9-159f48d60a0d3b7c980c6f3611197cc00da1772f.gz

\subsection{Hill climbing}
Hill climbing is an approximation that eliminates the need to maintain
a distance image. The approximation employed is that distances between
all neighbors in a 4, 6, 8, 18 or 26\footnote{4 and 8 connected
neighborhoods are used in 2D, 6, 18 and 26 in 3D} and the center of
the neighborhood are equal -- i.e the various $\sqrt{2}$ terms are
ignored. The position of the watershed lines can have some dependence
on raster ordering because of this. In general the approach is very
useful and efficient.

@@

\caption{Three difficult test images. The first image, plateau, illustrates a 
bad result produced by ITK's watershed in which most of the area is
assigned to one minima. This problem is also shown in Figure
\ref{fig:cthead1-markers}. The morphological watershed give a better
result, but not yet perfect: the separation line should not be curved
as it is. This problem is also visible in Figure
\ref{fig:embryo-mws}. The reason for the problem is as follows - the 
example is attempting to split a plateau into two regions, and should
therefore produce a Voronoi tesselation, with the two markers being
separated by a straight line. This does not happen because various
approximations have been made, as mentioned in Section \ref{}, that
influence the estimation of the distance function. Even if a more
accurate underlying distance function was used the computations are
still being carried out on a grid and so are limited by the digital
representation of lines.

The next image, thick line, again show that ITK watershed can produce
strange results with a green label which is where we should have the
light blue one. Morphological watershed gives good results. The last
image, button hole, is a very difficult case for watershed algorithms
which mark watershed lines: the watershed pixel at the bottom of the
image stop the label propagation. There are several possible
behaviors: produce a large watershed line which covers all the zone
(Vincent-Soille algorithm, not shown here), let the label on the top
of the image propagate into the zone (Meyer algorithm), split the zone
in 2 zones with the 2 labels of the bottom of the image (topological
watershed, not shown here).\label{fig:difficult-cases}}
\end{center}
\end{figure}

>>>>

\subsection{Hill climbing}
\label{sect:hillclimbing}
Hill climbing is an approximation that eliminates the need to maintain
a distance image. The approximation employed is that distances between
all neighbors in a 4, 6, 8, 18 or 26\footnote{4 and 8 connected
neighborhoods are used in 2D, 6, 18 and 26 in 3D} and the center of
the neighborhood are equal -- i.e the various $\sqrt{2}$ terms are
ignored. The position of the watershed lines can have some dependence
on raster ordering because of this. In general the approach is very
useful and efficient.

@@

\caption{Three difficult test images. The first image, plateau, illustrates a 
bad result produced by ITK's watershed in which most of the area is
assigned to one minima. This problem is also shown in Figure
\ref{fig:cthead1-markers}. The morphological watershed give a better
result, but not yet perfect: the separation line should not be curved
as it is. This problem is also visible in Figure
\ref{fig:embryo-mws}. The reason for the problem is as follows - the 
example is attempting to split a plateau into two regions, and should
therefore produce a Voronoi tesselation, with the two markers being
separated by a straight line. This does not happen because various
approximations have been made, as mentioned in Section
\ref{sect:hillclimbing}, that influence the estimation of the distance
function. Even if a more accurate underlying distance function was
used the computations are still being carried out on a grid and so are
limited by the digital representation of lines.
The next image, thick line, again show that ITK watershed can produce
strange results with a green label which is where we should have the
light blue one. Morphological watershed gives good results. The last
image, button hole, is a very difficult case for watershed algorithms
which mark watershed lines: the watershed pixel at the bottom of the
image stop the label propagation. There are several possible
behaviors: produce a large watershed line which covers all the zone
(Vincent-Soille algorithm, not shown here), let the label on the top
of the image propagate into the zone (Meyer algorithm), split the zone
in 2 zones with the 2 labels of the bottom of the image (topological
watershed, not shown here).\label{fig:difficult-cases}}
\end{center}
\end{figure}
